|

### 2021-04-09 02-Chp-Background.Rmd
End of day: -2681

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/background.R")

@@

### Diagnostic criteria

@@

While being widely cited and indeed included in a Cochrane review on this topic (ironically, the lead author on this Cochrane review is ), these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk. Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome. In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years. As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome. The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r mal::mal_estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.

@@

### Study designs

@@

<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias --->

@@

A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools). <!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience. --->

@@

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers in prevention science is currently under review at Prevention Science. This piece was co-written with Dr. Emily Hennessy (see author declarations). <!--- Will need to cross-reference this bit! --->

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/background.R")

@@

### Diagnostic criteria {#diagnostic-criteria}

@@

While being widely cited and indeed included in a Cochrane review on this topic (ironically, the lead author on this Cochrane review is ), these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk. Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome. In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years. As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome. The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.

@@

### Study designs and sources of bias

@@

<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias

In this context, assessment of

even within certain study designs, underlying biases are different

In some cases, synthesis across evidence required the

--->

@@

A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading). <!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience. --->

@@

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers in prevention science is currently under review at Prevention Science. This piece was co-written with Dr. Emily Hennessy (see Author Declarations in the front materials). <!--- Will need to cross-reference this bit! --->

### 2021-04-09 04-Chp-Systematic-Review.Rmd
End of day: -2681

@@

*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

-   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

@@

### Added evidental value of including preprints

@@

>>>>

<!--- Take a stand here! --->

Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes. While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up. While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)

This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.

Does it also cause issues in terms of self-report?

@@

As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

-   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult

@@

### Added evidental value of including preprints {}

@@

### Inclusion of preprints

As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted. Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.

The added evidental value of including these preprints was highlighted in Section

On further investigation, X of these preprints were subsequently published since the search was performed in 2019. While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.

### 2021-04-09 05-Chp-CPRD-Analysis.Rmd
Updates
End of day: 0
End of day: -2681

@@

@@

>>>>

<!-- Include the early analysis we did here, that did not work as a result of limited scope. Could include some of the genetic work also. Will additionally need to put the relevant materials from the paper in the  -->

@@

Expand on use of age as the time scale, but describe the problems this introduced

Expand on post estimation analyses, which showed that nothing except age had an effect.

@@

### Enabling easy synthesis

In light of my own experiences in attempting to extract information for papers assessing prevantive measures, I attempted to document

Study was reported in line with the [CHECK] reporting guidelines, and

### 2021-04-09 06-Chp-IPD-Analysis.Rmd
End of day: -2681

Letters sent to all cohorts identified through the

@@

Range of reasons why data is not made available.

@@

As part of this,

>>>>

Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all. Will also need to comment on the additional tactics used.

@@

Range of reasons why data is not readily available.

@@

### 2021-04-09 front-and-back-matter/_00-introduction.Rmd
All working again after the update to Pandoc
End of day: 0
End of day: -2681

@@

target <- (date_diff*200)+5580

@@

target_df <- data.frame(date = c(start_date,max_date),
                           words = c(5580, target))

@@

Words behind: `r words_behind`

@@

```{r word-count-fig, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(mapping = aes(x=date,y=words)) +
  geom_line(data = target_df, colour = "blue") +
  geom_step(data = words, colour = "red")

>>>>

files <- files[which(!(files %in% c("_main.Rmd","index.Rmd", "tmp.Rmd")))]

@@

target <- (date_diff*97) + 5580

@@

target_df <- data.frame(date = c(start_date,as.Date("20211116", format="%Y%m%d")),
                           words = c(5580, 40000))

@@

Words behind: `r format(words_behind, scientific = F)`

@@

```{r word-count-fig, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(mapping = aes(x=date,y=words)) +
  geom_line(data = target_df, colour = "black", linetype = 2) +
  geom_hline(yintercept = 40000, colour = "black", linetype = 2) +
  geom_vline(xintercept = as.numeric(as.Date("20211116", format="%Y%m%d")), colour = "black", linetype = 2) +
  geom_vline(xintercept = as.numeric(as.Date("20211216", format="%Y%m%d")), colour = "red") +
  scale_x_date(limits = c(as.Date("20201124", format="%Y%m%d"),as.Date("20211231", format="%Y%m%d"))) +
  geom_step(data = words, colour = "red")
